Project Setup

### 2024-11-29 setup.qmd
Use "data set" rather than "dataset"

Privacy laws and contractual obligations may require you to create a completely anonymized or synthetic dataset^[For example, using [Amnesia](https://amnesia.openaire.eu/), [ARX](https://arx.deidentifier.org/), [sdcMicro](https://sdctools.github.io/sdcMicro/), or [Synthpop](https://www.synthpop.org.uk/).] (if possible), or prohibit any sharing of data, in which case you should provide a reference to a data repository where they can be obtained from. For further information, you can watch the talk "[Data anonymity](https://osf.io/j6fy8)" by Felix Schönbrodt recorded during the LMU Open Science Center Summer School 2023 and have a look at [the accompanying slides](https://osf.io/z6gcu).

@@

```{.r filename="Console"}
table_info <- c(
  title = "penguins dataset",
  description = "Size measurements for adult foraging penguins near Palmer Station, Antarctica"
)
descriptions <- c(
  species = "a character string denoting penguin species",
  island = "a character string denoting island in Palmer Archipelago, Antarctica",
  bill_length_mm = "a number denoting bill length (millimeters)",
  bill_depth_mm = "a number denoting bill depth (millimeters)",
  flipper_length_mm = "an integer denoting flipper length (millimeters)",
  body_mass_g = "an integer denoting body mass (grams)",
  sex = "a character string denoting penguin sex",
  year = "an integer denoting the study year"
)
vals <- list(
  species = c("Adelie", "Gentoo", "Chinstrap"),
  island = c("Torgersen", "Biscoe", "Dream"),
  sex = c("male", "female"),
  year = c(2007, 2008, 2009)
)
```

>>>>

Privacy laws and contractual obligations may require you to create a completely anonymized or synthetic data set^[For example, using [Amnesia](https://amnesia.openaire.eu/), [ARX](https://arx.deidentifier.org/), [sdcMicro](https://sdctools.github.io/sdcMicro/), or [Synthpop](https://www.synthpop.org.uk/).] (if possible), or prohibit any sharing of data, in which case you should provide a reference to a data repository where they can be obtained from. For further information, you can watch the talk "[Data anonymity](https://osf.io/j6fy8)" by Felix Schönbrodt recorded during the LMU Open Science Center Summer School 2023 and have a look at [the accompanying slides](https://osf.io/z6gcu).

@@

```{.r filename="Console"}
table_info <- c(
  title = "penguins data set",
  description = "Size measurements for adult foraging penguins near Palmer Station, Antarctica"
)
descriptions <- c(
  species = "a character string denoting penguin species",
  island = "a character string denoting island in Palmer Archipelago, Antarctica",
  bill_length_mm = "a number denoting bill length (millimeters)",
  bill_depth_mm = "a number denoting bill depth (millimeters)",
  flipper_length_mm = "an integer denoting flipper length (millimeters)",
  body_mass_g = "an integer denoting body mass (grams)",
  sex = "a character string denoting penguin sex",
  year = "an integer denoting the study year"
)
vals <- list(
  species = c("Adelie", "Gentoo", "Chinstrap"),
  island = c("Torgersen", "Biscoe", "Dream"),
  sex = c("male", "female"),
  year = c(2007, 2008, 2009)
)
```
